Resilience and Home-Space for WSTS

### 2024-01-05 diapo/presentation.tex
up

Ideal =
\begin{itemize}
 \item downward-closed % is any set $D \subseteq X$ such that if $y \leq x$ and $x \in D$ then $y \in D $. 
 \item directed % i.e. it is nonempty and for every $a,b \in D$, there exists $c \in D$ such that $a \leq c$ and $b \leq c$.
\end{itemize}

  \todo[inline,color=blue!20]{ 
Définir Ideals and ideals.
}

@@

 effective = 
 \begin{itemize}
\item s $\to$ t decidable 
\item membership decidable 
\item $\leq$ decidable 
\item membership in $Ideals(S)$ decidable 
\item inclusion of ideals decidable
\end{itemize}

@@

@@

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Result C}

On On parle des VASS quand Safe downward closed

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Result C}

Définir rapidement les VASS

@@

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Result C}

>>>>

% Define WBSTS also ?

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Definitions}

Ideal =
\begin{itemize}
 \item Downward-closed % is any set $D \subseteq X$ such that if $y \leq x$ and $x \in D$ then $y \in D $. 
 ($y \leq x  \wedge x \in D \to y \in D$) 
 \item Directed % i.e. it is nonempty and for every $a,b \in D$, there exists $c \in D$ such that $a \leq c$ and $b \leq c$.
 ($D \neq \emptyset \wedge \forall a,b \in D, \exists c \in D, a \leq c \vee b \leq c$ )
\end{itemize}

@@

$S$ effective = 
 \begin{itemize}
\item $s \to t$ decidable 
\item membership decidable 
\item $\leq$ decidable 
\item membership in $Ideals(S)$ decidable 
\item inclusion of ideals decidable
\end{itemize}

@@

	$\to$ link between runs and runs of the completion (must define completion)

	$\to$ ideal decomposition of Bad

	$\to$ basis of Safe

	$\to$ coverability questions

	$\to$  resilience(s) can be reduced to coverability

@@

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Resilience for VASS}

% Définir rapidement les VASS

@@

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Resilience for VASS}
